E. coli resistance patterns from Community Resistance in Athens Project

### 2021-11-07 products/manuscript/Manuscript.Rmd
part 3: improvements, not final
manuscript and analysis

I am not including my data quite yet because I need to ensure that the IDs are changed so that we do not break our IRB agreement and to protect the identities of the individuals in the study. Once I have devised alternate IDs, I will upload data as 2 CSV files.

## Exploratory analysis

_Use a combination of text/tables/figures to explore and describe your data. You should produce plots or tables or other summary quantities for the most interesting/important quantities in your data. Depending on the total number of variables in your dataset, explore all or some of the others. FIgures produced here might be histograms or density plots, correlation plots, etc. Tables might summarize your data._

_Continue by creating plots or tables of the outcome(s) of interest and the predictor/exposure/input variables you are most interested in. If your dataset is small, you can do that for all variables. Plots produced here can be scatterplots, boxplots, violinplots, etc. Tables can be simple 2x2 tables or larger ones._

_To get some further insight into your data, if reasonable you could compute simple statistics (e.g. t-tests, simple regression model with 1 predictor, etc.) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p<0.05 means statistical significance" interpretation is not valid._

Table \@ref(tab:summarytable) shows a table summarizing the data.

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Data summary table.')
```

Figure \@ref(fig:resultfigure) shows a scatterplot figure produced by one of the R scripts.

```{r resultfigure,  fig.cap='Analysis figure.', echo=FALSE}
knitr::include_graphics("../../results/resultfigure.png")
```

@@

Example table \@ref(tab:resulttable) shows a table summarizing a linear model fit.

```{r resulttable,  echo=FALSE}
resulttable=readRDS("../../results/resulttable.rds")
knitr::kable(resulttable, caption = 'Linear model fit table.')
```

>>>>

@@

## Exploratory analysis
Load libraries
```{r}
library(tidyverse)
library(here)
library(knitr) #for inserting figures
```
The following figure explores the number of days in the last week participants ate a given food group. It appears most participants had some dairy in the last week, with most in the 7-day category. Poultry consumption seems to have a somewhat normal curve skewed left towards fewer days. 
```{r}
#Define food data location
fooddata_figure_location <- here::here("results","fooddata_figure.png")
#Load in saved image from results folder
include_graphics(fooddata_figure_location)
```
Compare the proportions of resistance to different antibiotics. Identify if there appear to be any correlations. Upon looking at all possible combinations, the following three were the only ones with enough data to possibly draw a trend.
```{r}
#Define amp_tet data location
amptet_figure_location <- here::here("results","amp_tet_plot.png")

#Define amp_tri data location
amptri_figure_location <- here::here("results","amp_tri_plot.png")

#Define tet_tri data location
tettri_figure_location <- here::here("results","tet_tri_plot.png")

#Load in saved image from results folder
include_graphics(amptet_figure_location)
include_graphics(amptri_figure_location)
include_graphics(tettri_figure_location)

```
Show fit between ampicillin and tetracycline, ampicillin and trimethoprim, and tetraycline and trimethoprim.
```{r}
#Define amp_tet fit data location
amptet_table_location <- here::here("results","amptettable.rds")
include_graphics(amptet_table_location)

````
# save ampicillin tetracycline fit results table  
amptettable_file = here("results", "amptettable.rds")
saveRDS(amptettable, file = amptettable_file)

# save ampicillin trimethoprim fit results table  
amptritable_file = here("results", "amptritable.rds")
saveRDS(amptritable, file = amptritable_file)

# save tetracycline trimethoprim fit results table  
tettritable_file = here("results", "tettritable.rds")
saveRDS(tettritable, file = tettritable_file)

#save ampicillin tetracycline figure results
amp_tet_plot_figure = here("results", "amp_tet_plot")
saveRDS(amp_tet_plot, file = amp_tet_plot_figure)

#save ampicillin trimethoprim figure results
amp_tet_plot_figure = here("results", "amp_tri_plot")
saveRDS(amp_tri_plot, file = amp_tri_plot_figure)

#save tetracycline trimethoprim figure results
amp_tet_plot_figure = here("results", "tet_tri_plot")
saveRDS(tet_tri_plot, file = tet_tri_plot_figure)

#save ampicillin-raw produce figure  
amp_produce_plot_figure = here("results", "amp_produce_plot")
saveRDS(amp_produce_plot, file = amp_produce_plot_figure)
